---
title: "PS07"
author: Cindy Zhang
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

#R packages:
library(ggplot2)
library(dplyr)
library(readr)
```

## GitHub Documents

This is an R Markdown format used for publishing markdown documents to GitHub. When you click the **Knit** button all R code chunks are run and a markdown file (.md) suitable for publishing to GitHub is generated.

## Including Code

You can include R code in the document as follows:

```{r cars}
smith_admission <- read_csv("/Users/cindyzhang/Desktop/Smith Class/2021 Fall/SDS 192/Problem Set/PS07/smith_admission.csv")
```

## Including Plots

You can also embed plots, for example:

```{r pressure, echo=FALSE}
ggplot(data = smith_admission, 
       mapping = aes(x = Year, y = Acceptance_Rate)) +
  ylim(25, 55) +
  ylab("Acceptance Rate") +
  labs(title = "Smith College Undergraduate Admission Acceptance Rate", subtitle = "from 2011-2021") +
  geom_text(aes(label = Acceptance_Rate), size = 3, vjust = -1.3) +
  geom_line()
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
